Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-19 analysis/paper/paper.qmd
Edit two boxplots for temporal pattern

temporal_tcsa +
 annotate("rect", 
           xmin = 0,
           xmax = 12.2,
           ymin = 0,
           ymax = 300,
           fill = "green",
           alpha = 0.2) +
  annotate("text", 
               size = 3.5,
               label = "MIS 3",
               hjust = 0,
           x = 5,
           y = 260) +
   annotate("rect", 
           xmin = 12.2,
           xmax = 24.5,
           ymin = 0,
           ymax = 300,
           fill = "yellow",
           alpha = 0.2) +
  annotate("text", 
               size = 3.5,
               label = "MIS 2",
               hjust = 0,
           x = 17,
           y = 260) +
   annotate("rect", 
           xmin = 13.5,
           xmax = 21,
           ymin = 0,
           ymax = 230,
           fill = "yellow",
           alpha = 0.2) +
  annotate("text", 
               size = 2.3,
               label = "LGM",
               hjust = 0,
           x = 17.3,
           y = 210)

@@

# aggregate all the MIS 3 sites, MIS 2 sites
tcsa_site_ass_mis <- tcsa_site_ass %>% 
                      mutate(mis_stage = case_when (
                        age_ka > 29 ~ '3', age_ka < 29 ~ '2'))

# box plot for each MIS stage
  ggplot(tcsa_site_ass_mis, 
       aes(y = min_tcsa,
           x = mis_stage)) +
   geom_boxplot() +
   theme_minimal() +
   theme(legend.position="none") +
   labs(y = "TCSA", 
        x = "MIS") +
  geom_quasirandom(alpha = 0.4,
                   size = 2.3) +
    scale_x_discrete(limits=rev) +
     annotate("rect", 
           xmin = 2.1,
           xmax = 2.2,
           ymin = 4,
           ymax = 18,
           fill = "green",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Poisoned\narrow tips",
               hjust = 0,
               lineheight = 0.75,
           x = 2.1,
           y = (18-4) /2 + 4) +
      annotate("rect", 
           xmin = 2.2,
           xmax = 2.3,
           ymin = 17,
           ymax = 47,
           fill = "blue",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Un-poisoned\narrow tips",
               hjust = 0,
               lineheight = 0.75,
           x = 2.2,
           y = (47-17) /2 + 17) +
      annotate("rect", 
           xmin = 2.3,
           xmax = 2.4,
           ymin = 40,
           ymax = 76,
           fill = "orange",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Dart tips",
               hjust = 0,
           x = 2.3,
           y = (76-40) /2 + 40) +
      annotate("rect", 
           xmin = 2.4,
           xmax = 2.5,
           ymin = 42,
           ymax = 90,
           fill = "purple",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Javelin tips",
               hjust = 0,
           x = 2.4,
           y = (90-42) /2 + 42) +
     annotate("rect", 
           xmin = 2.5,
           xmax = 2.6,
           ymin = 80,
           ymax = 200,
           fill = "yellow",
           alpha = 0.2) +
      annotate("text", 
               label = "Stabbing\nspear tips",
               size = point_function_group_label_size,
               hjust = 0,
               lineheight = 0.75,
           x = 2.5,
           y = (200-80) /2 + 80 )

>>>>

temporal_tcsa +
 annotate("rect", 
           xmin = 0,
           xmax = 12.2,
           ymin = 0,
           ymax = 300,
           fill = "lightgray",
           alpha = 0.2) +
  annotate("text", 
               size = 3.5,
               label = "MIS 3",
               hjust = 0,
           x = 5,
           y = 260) +
   annotate("rect", 
           xmin = 12.2,
           xmax = 24.5,
           ymin = 0,
           ymax = 300,
           alpha = 0.2) +
  annotate("text", 
               size = 3.5,
               label = "MIS 2",
               hjust = 0,
           x = 17,
           y = 260) +
   annotate("rect", 
           xmin = 13.5,
           xmax = 21,
           ymin = 0,
           ymax = 230,
           alpha = 0.2) +
  annotate("text", 
               size = 2.3,
               label = "LGM",
               hjust = 0,
           x = 17.3,
           y = 210)

@@

# aggregate all the MIS 3 sites, MIS 2 sites
tcsa_site_ass_mis <- tcsa_site_ass %>% 
                      mutate(mis_stage = case_when (
                        age_ka > 26.5 ~ 'Before' , age_ka > 19 ~ 'LGM', age_ka < 19 ~ 'After'))

# box plot for each MIS stage
  ggplot(tcsa_site_ass_mis, 
       aes(y = min_tcsa,
           x = factor(mis_stage, level = c('After', 'LGM', 'Before')))) +
   geom_boxplot() +
   theme_minimal() +
   theme(legend.position="none") +
   labs(y = "TCSA", 
        x = "MIS") +
  geom_quasirandom(alpha = 0.4,
                   size = 2.3) +
    scale_x_discrete(limits=rev) +
     annotate("rect", 
           xmin = 3.4,
           xmax = 3.5,
           ymin = 4,
           ymax = 18,
           fill = "green",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Poisoned\narrow tips",
               hjust = 0,
               lineheight = 0.75,
           x = 3.4,
           y = (18-4) /2 + 4) +
      annotate("rect", 
           xmin = 3.5,
           xmax = 3.6,
           ymin = 17,
           ymax = 47,
           fill = "blue",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Un-poisoned\narrow tips",
               hjust = 0,
               lineheight = 0.75,
           x = 3.5,
           y = (47-17) /2 + 17) +
      annotate("rect", 
           xmin = 3.6,
           xmax = 3.7,
           ymin = 40,
           ymax = 76,
           fill = "orange",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Dart tips",
               hjust = 0,
           x = 3.6,
           y = (76-40) /2 + 40) +
      annotate("rect", 
           xmin = 3.7,
           xmax = 3.8,
           ymin = 42,
           ymax = 90,
           fill = "purple",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Javelin tips",
               hjust = 0,
           x = 3.7,
           y = (90-42) /2 + 42) +
     annotate("rect", 
           xmin = 3.8,
           xmax = 3.9,
           ymin = 80,
           ymax = 200,
           fill = "yellow",
           alpha = 0.2) +
      annotate("text", 
               label = "Stabbing\nspear tips",
               size = point_function_group_label_size,
               hjust = 0,
               lineheight = 0.75,
           x = 3.8,
           y = (200-80) /2 + 80 )
